---
title: "Assignment2"
author: "Namgyu Han"
date: '2021 9 7 '
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1

This exercise relates to the College data set, which can be found in the file College.csv uploaded on the course’s public webpage (https://scads.eecs.wsu.edu/wp- content/uploads/2021/09/College.csv). The dataset contains a number of variables for 777 different universities and colleges in the US. The variables are

•	Private : Public/private indicator

•	Apps : Number of applications received

•	Accept : Number of applicants accepted

•	Enroll : Number of new students enrolled

•	Top10perc : Percentage of new students from top 10% of high school class

•	Top25perc : Percentage of new students from top 25% of high school class

•	F.Undergrad : Number of full-time undergraduates

•	P.Undergrad : Number of part-time undergraduates

•	Outstate : Out-of-state tuition

•	Room.Board : Room and board costs

•	Books : Estimated book costs

•	Personal : Estimated personal spending

•	PhD : Percent of faculty with Ph.D.’s

•	Terminal : Percent of faculty with terminal degree

•	S.F.Ratio : Student/faculty ratio

•	perc.alumni : Percent of alumni who donate

•	Expend : Instructional expenditure per student

•	Grad.Rate : Graduation rate


Before reading the data into R or Python, you can view it in Excel or a text editor. For each of the following questions, include the code you used to complete the task as your response, along with any plots or numeric outputs produced. You may omit outputs that are not relevant (such as dataframe contents), but still include all of your code.


(a)	Use the read.csv() function to read the data into R, or the csv library to read in the data with python. In R you will load the data into a dataframe. In python you may store it as a list of lists or use the pandas dataframe to store your data. Call the loaded data college. Ensure that your column headers are not treated as a row of data.

```{r}
College = read.csv(file="C:/Users/user/sample/College.csv",sep=",", header=TRUE)
summary(College)
```



(b)	Find the median cost of room and board (Room.Board) for all schools in this dataset. Then find the median cost of room and board (Room.Board) for both public and private (Private) schools.

```{r}
print(median(College$Room.Board))
```



(c)	Produce a scatterplot that shows a relationship between two numeric (not factor or boolean) features of your choice in the dataset. Ensure it has appropriate axis labels and a title.

```{r}
library(ggplot2)

relation <- College[,c("Top10perc","PhD")]

ggplot(relation, aes(x= Top10perc, y= PhD)) + geom_point() + labs(title = "Scatter Plot: Between (Top 10 new student ratio) and (Ph.D. ratio)", x="New student ratio who top 10 percent of high school", y="University's Ph.D. faculty ratio") + theme(plot.title = element_text(hjust = 0.5))
```



(d)	Produce a histogram showing the overall enrollment numbers (P.Undergrad plus F.Undergrad) for both public and private (Private) schools. You may choose to show both on a single plot (using side by side bars) or produce one plot for public schools and one for private schools. Ensure whatever figures you produce have appropriate axis labels and a title.

```{r}
College$Overall <- (College$P.Undergrad + College$F.Undergrad)

ggplot(College, aes(x=Overall, fill=Private)) + geom_histogram(bins=15,position="dodge") + labs(title = "Private/Public School The Overall Enrollment numbers", x="Overall Enrollment numbers", y="University numbers") + theme(plot.title = element_text(hjust = 0.5))
```



(e)	Create a new qualitative variable, called Top, by binning the Top10perc variable into two categories (Yes and No). Specifically, divide the schools into two groups based on whether or not the proportion of students coming from the top 10% of their high school classes exceeds 75%.
Now produce side-by-side boxplots of the schools' acceptance rates (based on Accept and Apps) for each of the two Top categories. There should be two boxes on your figure, one for top schools and one for others. How many top universities are there?

```{r}
College$Top <- rep("No",nrow(College))
College$Top[College$Top10perc>75] = "Yes"
College$div <- rep("0",nrow(College))
College$div[College$Top == "Yes"] = 1
College$AcptRate <- (College$Accept / College$Apps)

ggplot(College, aes(x=div, y=AcptRate, color=Top)) + geom_boxplot() + labs(title = "Acceptance rate for Top and other schools", x="Scool Rank", y="Acceptance rate") + scale_color_manual(name="School Rank", labels=c("Others", "Top Schools"), values=c("orange","red"))
```


The number of Top school:
```{r}
length(which(College$Top=="Yes"))
```




(f)	Continue exploring the data, producing two new plots of any type, and provide a brief (one to two sentence) summary of your hypotheses and what you discover. Feel free to think outside the box on this one but if you want something to point you in the right direction, look at the summary statistics for various features, and think about what they tell you. Perhaps try plotting various features from the dataset against each other and see if any patterns emerge.

```{r}
ggplot(College, aes(x=Grad.Rate, fill=Private)) + geom_histogram(bins=15,position="dodge") + labs(title = "Comparing Graduation rate of Private School and Public Scool)", x="Graduation rate", y="University's counts") + theme(plot.title = element_text(hjust = 0.5))

ggplot(College, aes(x=Expend, fill=Private)) + geom_histogram(bins=15,position="dodge") + labs(title = "Comparing Instructional expenditure per student of Private School and Public Scool)", x="Instructional expenditure per student", y="University's counts") + theme(plot.title = element_text(hjust = 0.5))

relation <- College[,c("Grad.Rate","Expend")]

ggplot(relation, aes(x= Grad.Rate, y= Expend)) + geom_point() + labs(title = "Relationship between Instructional expenditure per student and Graduation rate)", x="Instructional expenditure per student", y="University's counts") + theme(plot.title = element_text(hjust = 0.5))
```


The Mean of Private school's graduation rate:
```{r}
mean(College$Grad.Rate[College$Private == "Yes"])
```


The Mean of Public school's graduation rate:
```{r}
mean(College$Grad.Rate[College$Private == "No"])
```


The Mean of Private school's Instructional expenditure per student:
```{r}
mean(College$Expend[College$Private == "Yes"])
```


The Mean of Public school's Instructional expenditure per student:
```{r}
mean(College$Expend[College$Private == "No"])
```


```{r}
ggplot(College, aes(x=Grad.Rate, y=Expend, color=Private)) + geom_point()
```


I suppose there is some difference between private school and public school. From the dataset, I thought the difference would be in the graduation rate and the instructional expenditure per student. So, I made three graphs. 

The first graph is a histogram showing the graduation rates of private and public schools. The second graph is a histogram showing the instructional expenditure per student of each private and public school. Using the results of these two histograms, I tried to express the relationship between the graduation rate and the instructional expenditure per student in plotting graph, but it was difficult to find significant results from the graph.
However, in fact, the graduation rate of private schools (69%) was higher than that of public schools (56.04%), and the graduation rate of private schools (10486.35$) was higher than that of public schools (7458.32$).

So, I made new plotting graph which distinguishes color of private and public school. It's not clear, but shows little difference between private and public school.








## 2

This exercise involves the forestfires.csv dataset that can be loaded into a dataframe from (https://scads.eecs.wsu.edu/wp-content/uploads/2021/09/forestfires.csv). The features of the dataset are:

•	month: month of the year

•	day: day of the week

•	FFMC: Fine Fuel Moisture Code index

•	DMC: Duff Moisture Code index

•	DC: Drought code index

•	ISI: Initial spread index

•	temp: Temperature in degrees Celsius

•	RH: Relative Humidity

•	wind: Wind speed (km/h)

•	rain: Amount of rainfall (mm/m2)

•	area: area that got burnt in the forest fire
 
 
Make sure that rows with missing values have been removed from the data. Show both the code you used and any relevant outputs.

```{r}
Forestfire = read.csv(file="C:/Users/user/sample/forestfires.csv",sep=",", header=TRUE)
```



(a)	Specify which of the predictors are quantitative (measuring numeric properties such as size, or quantity), and which are qualitative (measuring non-numeric properties such as color, appearance, type etc.), if any? Keep in mind that a qualitative variable may be represented as a quantitative type in the dataset, or the reverse. You may wish to adjust the types of your variables based on your findings.


In the data table..

- The quantitative variable can be: FFMC, DMC, DC, ISI, Temperature, Relative humidity, Wind speed, Amount of rainfall, and Area.

- The qualitative variable can be: Month and Day




(b)	What is the range, mean and standard deviation of each quantitative predictor?

Range:
```{r}
sapply(Forestfire[,c(3:11)], range)
```

Mean:
```{r}
sapply(Forestfire[,c(3:11)], mean)
```

Standard Deviation
```{r}
sapply(Forestfire[,c(3:11)], sd)
```




(c)	Now remove the 20th through 70th (inclusive) observations from the dataset. What is the range, mean, and standard deviation of each predictor in the subset of the data that remains?

```{r}
sForestfire <- Forestfire[-c(20:70),]
```

Range:
```{r}
sapply(sForestfire[,c(3:11)], range)
```

Mean:
```{r}
sapply(sForestfire[,c(3:11)], mean)
```

Standard Deviation
```{r}
sapply(sForestfire[,c(3:11)], sd)
```




(d)	Produce a bar plot to show the count of forest fires in each month. During which months are forest fires most common? (Hint: group data by month and calculate count)

```{r}
Forestfire$fire <- rep(0,nrow(Forestfire))
Forestfire$fire[Forestfire$area > 0] = 1

numfire <- subset(Forestfire, fire == 1)

ggplot(numfire, aes(month)) + geom_bar() + labs(title = "The number of forestfires per month", x="Month", y="Count")
```

- August is forest fires most common


(e)	Using the full data set, investigate the predictors graphically, using scatterplots, correlation scores or other tools of your choice. Create a correlation matrix for the relevant variables.

```{r}
library(ggcorrplot)

quant <- Forestfire[-c(1,2,12)]

plot(quant)
corr <- cor(quant)
corr

ggcorrplot(corr)
```




(f)	Suppose that we wish to predict the area burned by the forest fire (area) on the basis of the other variables. Which, if any, of the other variables might be useful in predicting area? Justify your answer based on the prior correlations.

- According to the correlation plot based on the scatter plot, temperature(positive relation) and relative humidity(negative relation) have high correlation with the area burned by the forest fire.
